A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-11 tex/main.tex
Add an abstract.

\abstract{TBD}

>>>>

\abstract{The Iterated Prisoner's Dilemma is a well established framework for
          the study of emergent behaviour. In this paper an extensive numerical
          study of the evolutionary dynamics of this framework are presented.

          Fixation probabilities for Moran processes are obtained for 172
          different strategies. This is done in both a standard 200 turn
          interaction and a noisy setting.

          To the authors knowledge this is the largest
          such study. It allows for insights about the behaviour and
          performance of strategies with regard to their survival in an
          evolutionary setting.
          }  % TODO Add main conclusion/finding.
